Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-09-02 WSSSPE3/report/wg_appendix_software_credit.tex
fixing bib to more recent version

\item Transitive credit~\cite{wssspe2_katz,Katz:2014_tc}, which assigns
contriponents (contributors and components) various weights depending on their
level of importance;

@@

At a minimum, the metadata required for software citation includes:
\begin{itemize}
    \item Name of software,
    \item DOI for software,
    \item Contributors, in the form of names and ORCIDs,
    \item Software dependencies, in the form of DOIs, and
    \item Other people and artifacts that would be cited or acknowledged in a paper.
\end{itemize}
This information would then be contained in a citation file, e.g., as part of
the GitHub repository. The group also discussed similar efforts such as
CodeMeta\footnote{CodeMeta: \url{https://github.com/codemeta/codemeta}}, an
attempt to codify minimal metadata schemes in JSON and XML for scientific
software and code, and implementing transitive credit via
JSON-LD~\cite{wssspe2_katz}. Some questions arose about how this information
would be stored for closed-source software.

>>>>

\item Transitive credit~\cite{Katz:2014_tc,katz-smith-tc}, which assigns
contriponents (contributors and components) various weights depending on their
level of importance;

@@

At a minimum, the metadata required for software citation includes:
\begin{itemize}
    \item Name of software,
    \item DOI for software,
    \item Contributors, in the form of names and ORCIDs,
    \item Software dependencies, in the form of DOIs, and
    \item Other people and artifacts that would be cited or acknowledged in a paper.
\end{itemize}
This information would then be contained in a citation file, e.g., as part of
the GitHub repository. The group also discussed similar efforts such as
CodeMeta\footnote{CodeMeta: \url{https://github.com/codemeta/codemeta}}, an
attempt to codify minimal metadata schemes in JSON and XML for scientific
software and code, and implementing transitive credit via
JSON-LD~\cite{katz-smith-tc}. Some questions arose about how this information
would be stored for closed-source software.

### 2016-09-02 WSSSPE3/report/wg_main_software_credit.tex
fixing bib to more recent version

The group discussed a number of topics related to software credit, including a
contributorship taxonomy, software citation metadata, standards for citing
software in publications, and increasing the value of software in academic
promotion and tenure reviews. Although initial discussions both prior to and
during WSSSPE3 focused on contribution taxonomy and dividing credit, discussing
as an example the Entertainment Identifier Registry~\cite{EIDR} used in the
entertainment industry, the group decided to prioritize software citation. This
decision was motivated by the idea that standardizing citations for software
would introduce some initial credit for developers, and later the quantification
of credit could be refined based on concepts such as transitive
credit~\cite{wssspe2_katz,Katz:2014_tc}.

>>>>

The group discussed a number of topics related to software credit, including a
contributorship taxonomy, software citation metadata, standards for citing
software in publications, and increasing the value of software in academic
promotion and tenure reviews. Although initial discussions both prior to and
during WSSSPE3 focused on contribution taxonomy and dividing credit, discussing
as an example the Entertainment Identifier Registry~\cite{EIDR} used in the
entertainment industry, the group decided to prioritize software citation. This
decision was motivated by the idea that standardizing citations for software
would introduce some initial credit for developers, and later the quantification
of credit could be refined based on concepts such as transitive
credit~\cite{Katz:2014_tc,katz-smith-tc}.
